Using algorithmic skeletons in EcmaScript to parallelize computation in browsers through Web Workers

### 2015-05-16 docs/paper/paper.tex
Minor fix
Updated all current benchmarks to use FF 41

To verify our hypothesis, we put together two benchmarks\footnote{All benchmarks in this document use the environment described in Tab.~\ref{tab:env}.} that aim to verify the difference between invoking \verb+postMessage+ with and without structured cloning for a \verb+SharedTypedArray+. Both transfer a \verb+SharedTypedArray+ back and forth between the UI thread and a worker; the only difference between the two is that one has 100,000 (a hundred thousand) elements in the \verb+SharedTypedArray+ and the other one 1,000,000 (a million). As it can be seen from the  results in Tab.~\ref{tab:transf-vs-clone}, increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \verb+Transferable+ objects, it scales. On the other hand, the amount of operations that can be performed with structured cloning greatly decreases.

@@

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    Elements & Cloning [ops/sec] & Transferring [ops/sec] \\
    \hline
    \(1E5\) & 972 & \textbf{1705} \\
    \(1E6\) & 114 & \textbf{754} \\
    \hline
  \end{tabular}
  \caption{Difference between transferring and cloning shared buffers.}
  \label{tab:transf-vs-clone}
\end{table}

@@

The benchmarks provided the following results:
\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    Native encoding API [ops/sec] & Non-native function [ops/sec] \\
    \hline
    \textbf{5247} & 4685 \\
    \hline
  \end{tabular}
  \caption{Difference encoding/decoding strings natively and in JavaScript.}
  \label{tab:encode-decode}
\end{table}

@@

We created a benchmark using two functions whose string representation has different lengths to see if the function's length affected the serialization and transfer time (results in Tab.~\ref{tab:send-function}). We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \verb+String+ into an \verb+TypedArrayBuffer+, sending it as a \verb+Tranferable+ and decoding it on the Web Worker.
  \item Sending the \verb+String+ directly.
  \item Using a \verb+Blob+ to store the stream and retrieving that in the Worker.
\end{enumerate}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Function length & Blob [ops/sec] & Copy [ops/sec] & Tranferable [ops/sec] \\
    \hline
    Short & 1251 & \textbf{7046} & 6219 \\
    Long & 705 & 1176 & \textbf{1198} \\
    \hline
  \end{tabular}
  \caption{Sending function strings from UI thread to Web Workers.}
  \label{tab:send-function}
\end{table}

We also created a benchmark that tranfers a \verb+SharedTypedArray+ and a \verb+String+ that are properties of the same \verb+message+ object back and forth between the UI thread an a Web Worker to understand if transferring additional objects affected the transfer time when comparing it with just tranferring a \verb+String+ (results in Tab.~\ref{tab:send-function-and-array}.
\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    Copying code [ops/sec] & Tranferring code [ops/sec] \\
    \hline
    4200 & \textbf{4340} \\
    \hline
  \end{tabular}
  \caption{Sending code and a TypedArray to a Web Worker.}
  \label{tab:send-function-and-array}
\end{table}

@@

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{142223} & 328 \\
    1,000 & \textbf{16503.8} &  359 \\
    10,000 & \textbf{1683.8} & 321.8 \\
    100,000 & \textbf{169.6} & 184.4 \\
    1,000,000 & 16.8 & \textbf{34.1} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

>>>>

To verify our hypothesis, we put together two benchmarks\footnote{All benchmarks in this document use the environment described in Tab.~\ref{tab:env}.} that aim to verify the difference between invoking \verb+postMessage+ with and without structured cloning for a \verb+SharedTypedArray+. Both transfer a \verb+SharedTypedArray+ back and forth between the UI thread and a worker; the only difference between the two is that one\footnote{http://jsperf.com/transferrable-vs-cloning/2} has 100,000 (a hundred thousand) elements in the \verb+SharedTypedArray+ and the other one\footnote{http://jsperf.com/longer-transferrable-vs-cloning/2} 1,000,000 (a million). As it can be seen from the  results in Tab.~\ref{tab:transf-vs-clone}, increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \verb+Transferable+ objects, it scales. On the other hand, the amount of operations that can be performed with structured cloning greatly decreases.

@@

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    Elements & Cloning [ops/sec] & Transferring [ops/sec] \\
    \hline
    \(1E5\) & 734 & \textbf{1596} \\
    \(1E6\) & 91 & \textbf{1134} \\
    \hline
  \end{tabular}
  \caption{Difference between transferring and cloning shared buffers.}
  \label{tab:transf-vs-clone}
\end{table}

@@

The results for the benchmark\footnote{http://jsperf.com/pjs-serialization-comparison/2} are in Tab.~\ref{tab:encode-decode}:
\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    Native encoding API [ops/sec] & Non-native function [ops/sec] \\
    \hline
    \textbf{5017} & 4398 \\
    \hline
  \end{tabular}
  \caption{Difference encoding/decoding strings natively and in JavaScript.}
  \label{tab:encode-decode}
\end{table}

@@

We created benchmarks\footnote{http://jsperf.com/pjs-serialization-long/3 and http://jsperf.com/pjs-serialization/3} using two functions whose string representation has different lengths to see if the function's length affected the serialization and transfer time (results in Tab.~\ref{tab:send-function}). We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \verb+String+ into an \verb+TypedArrayBuffer+, sending it as a \verb+Tranferable+ and decoding it on the Web Worker.
  \item Sending the \verb+String+ directly.
  \item Using a \verb+Blob+ to store the stream and retrieving that in the Worker.
\end{enumerate}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Function length & Blob [ops/sec] & Copy [ops/sec] & Tranferable [ops/sec] \\
    \hline
    Short & 1070 & \textbf{6629} & 5927 \\
    Long & 1075 & \textbf{3273} & 2967 \\
    \hline
  \end{tabular}
  \caption{Sending function strings from UI thread to Web Workers.}
  \label{tab:send-function}
\end{table}

We also created a benchmark\footnote{http://jsperf.com/pjs-encoding/2} that tranfers a \verb+SharedTypedArray+ and a \verb+String+ that are properties of the same \verb+message+ object back and forth between the UI thread an a Web Worker to understand if transferring additional objects affected the transfer time when comparing it with just tranferring a \verb+String+ (results in Tab.~\ref{tab:send-function-and-array}.
\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    Copying code [ops/sec] & Tranferring code [ops/sec] \\
    \hline
    \textbf{4509} & 4270 \\
    \hline
  \end{tabular}
  \caption{Sending code and a TypedArray to a Web Worker.}
  \label{tab:send-function-and-array}
\end{table}

@@

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{142223} & 328 \\
    1,000 & \textbf{16503.8} &  359 \\
    10,000 & \textbf{1683.8} & 321.8 \\
    100,000 & 169.6 & \textbf{184.4} \\
    1,000,000 & 16.8 & \textbf{34.1} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}
